Evaluation

### 2018-02-19 evaluation.Rmd
Correctly state that prediction intervals are 90% in evaluation
The prediction intervals have always been 90%, but they were described and shown
as 95%. This fixes this issue and in the process creates a new metadata value
for the prediction interval (thanks to @ha0ye's suggestion) that can be used
throughout the code base. Updates to the models will be necessary to use this
value for all instances of prediction interval in the code base.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(portalr)
source("tools/forecast_tools.R")

models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

@@

**RMSE**: Root mean square error, this is a metric used to evaluate the point estimate of a forecast.  
**Coverage**: This is the percentage of observations which fell within the 95% confidence interval of a forecast. Ideally this would be equal to 0.95. If it's higher than 0.95 the forecasts intervals are too wide, if it's lower then the forecast intervals are too narrow.

@@

ggplot(forecast_errors, aes(x=lead_time, y=error_value, group=model, color=model)) +
  geom_point()+
  geom_line() +
  geom_hline(yintercept = 0.95) +
  labs(x='Lead Time (New Moons)') +
  facet_wrap(full_species_name~error_metric, scales = 'free_y', ncol=2) + 
  theme_bw() +
  labs(y = "Error Value", colour = "Model")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(portalr)
library(yaml)
source("tools/forecast_tools.R")

model_metadata = yaml.load_file("data/model_metadata.yaml")
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

@@

**RMSE**: Root mean square error, this is a metric used to evaluate the point estimate of a forecast.  
**Coverage**: This is the percentage of observations which fell within the `r 100 * pred_interval`% confidence interval of a forecast. Ideally this would be equal to `r pred_interval`. If it's higher than `r pred_interval` the forecasts intervals are too wide, if it's lower then the forecast intervals are too narrow.

@@

ggplot(forecast_errors, aes(x=lead_time, y=error_value, group=model, color=model)) +
  geom_point()+
  geom_line() +
  geom_hline(yintercept = 0.9) +
  labs(x='Lead Time (New Moons)') +
  facet_wrap(full_species_name~error_metric, scales = 'free_y', ncol=2) + 
  theme_bw() +
  labs(y = "Error Value", colour = "Model")
